The impact of cosmic variance on simulating weak lensing surveys

### 2014-11-12 Writeup/paper_v3.tex
Quantitative statement about mass dist.

We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
indices of the stellar mass-selected samples (\s$3$) are
systematically greater than those of the luminosity selected samples
(\s$1$, \s$2$).  
This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of the galaxies extends to $\log(M/M_\odot) \sim 9.0$.
It is therefore not surprising that \s3 has a higher median \sersic $n$.  Finally, even for
the stellar mass-selected sample there is some sign of redshift
evolution.  The sign of this evolution is as expected, with lower
\sersic $n$ and $B/T$ for higher redshift samples, which should have a
higher fraction of disk and irregular galaxies and fewer galaxies with
bulge-like morphology.

>>>>

We also note that in Fig.~\ref{fig:median_sersicn}, the median \sersic
indices of the stellar mass-selected samples (\s$3$) are
systematically greater than those of the luminosity selected samples
(\s$1$, \s$2$).  
This is because \s3 is restricted to galaxies with masses above $\log(M/M_\odot) > 10.15$, whereas in \s1 and \s2, the mass distribution of galaxies extends to $\log(M/M_\odot) \sim 9.0$,
with about 44 per cent of the galaxies in \s2 below the stellar mass cut placed for \s3.
It is therefore not surprising that \s3 has a higher median \sersic $n$.  Finally, even for
the stellar mass-selected sample there is some sign of redshift
evolution.  The sign of this evolution is as expected, with lower
\sersic $n$ and $B/T$ for higher redshift samples, which should have a
higher fraction of disk and irregular galaxies and fewer galaxies with
bulge-like morphology.
